Towards Comparable Active Learning

### 2023-06-04 doc/al_benchmark_paper.tex
paper update

\subsection*{Contributions}
\begin{enumerate}
	\item Evaluation of Active Learning algorithms on datasets from 3 different domains, including synthetic data that highlights principled shortcomings of existing approaches.
	\item Novel experimental protocol for controlling AL experiments to allow full reproducibility.
	\item Simple algorithm for an Oracle that can be constructed greedily and does not rely on search.
\end{enumerate}

>>>>

\subsection*{Contributions}
\begin{enumerate}
	\item Evaluation of Active Learning algorithms on datasets from 3 different domains
	\item Two novel synthetic dataset that highlight principled shortcomings of existing AL algorithms
	\item Novel experimental protocol for controlling AL experiments to allow full reproducibility
	\item Simple algorithm for an Oracle that can be constructed greedily and does not rely on search
\end{enumerate}
